---
title: "R Cheat Sheets & Notes"
---

## Cheat Sheets

* [R Colors](http://www.stat.columbia.edu/~tzheng/files/Rcolor.pdf)

* [R Base Graphics Cheat Sheet](http://www.joyce-robbins.com/wp-content/uploads/2016/04/BaseGraphicsCheatsheet.pdf)

* [R Base Commands Cheat Sheet](https://www.rstudio.com/wp-content/uploads/2016/10/r-cheat-sheet-3.pdf)

* [R Markdown Cheat Sheet](https://www.rstudio.com/wp-content/uploads/2015/02/rmarkdown-cheatsheet.pdf)

* [Keyboard Shortcuts](https://support.rstudio.com/hc/en-us/articles/200711853-Keyboard-Shortcuts)

* [R ggplot2 Cheat Sheet](https://r-graph-gallery.com/)

## Notes

                          Parametric         | non-parametric
One Sample              | One Sample t-test  | Wilcoxon Signed-Rank
Two Sample: Dependent   | paired t-test      | Wilcoxon Signed-Rank
Two Sample: Independent | independent t-test | Wilcoxon Mann Whitney
Three Samples           | One-way ANOVA      | Kruskal Wallis

```{r}
# Add R commands you want to remember here...
# 
#                           Parametric         | non-parametric
# One Sample              | One Sample t-test  | Wilcoxon Signed-Rank
# Two Sample: Dependent   | paired t-test      | Wilcoxon Signed-Rank
# Two Sample: Independent | independent t-test | Wilcoxon Mann Whitney
# Three Samples           | One-way ANOVA      | Kruskal Wallis
```

```{r}
# Or create other R chunks to put them in like this...

```

```{r, eval=FALSE}
# Using ```{r, eval=FALSE} turns off the chunk, but still shows it.
# Useful when you want to remember code, but not run it in this file.
```




```{r, eval=FALSE}

```




