---
title: "High School Seniors t Test"
output: 
  html_document:
    theme: cerulean
    code_folding: hide
---

```{r, message=FALSE, warning=FALSE}
library(tidyverse)
library(DT)
library(pander)
library(readr)
library(mosaic)

HSS <- read_csv("../../Data/HighSchoolSeniors.csv")
#Remember: select "Session, Set Working Directory, To Source File Location", and then play this R-chunk into your console to read the HSS data into R. 
```

<!-- Instructions

1. Use the HSS dataset in R to come up with a question that can be answered with a t Test. 

Who sends more texts on average in a given day between women and men.


Here is a link to the survey given to the students that participated in the study:
https://ww2.amstat.org/censusatschool/pdfs/C@SQuestionnaire.pdf
(Use the link to learn about what each column of data in the data set represents.)

2. Establish why your question is interesting and rephrase the question using a statistical "null" and "alternative" hypothesis. (Hint, see the "Math 325 Notebook -> R Help -> R-Markdown Hints" page of your textbook for instructions on how to write mathematical hypotheses.)

This question is interesting because there is sometimes a stereotype that high school girls are always texting. It would be interesting to see if this stereotype holds true when comparing to men of the same age group. 
$$
  H_0: \mu_\text{Women} = \mu_\text{Men}
  H_a: \mu_\text{Women} \gt \mu_\text{Men}
$$

3. Clearly answer your question using statistics. Be sure to compute a p-value and provide supporting numerical and graphical summaries.



Note: you can create "groups" from the data in many ways. For example, suppose you wanted to create a variable that grouped people according to whether they thought recycling was more important than conserving water. You could do this by:



```{r}
HSS <- HSS %>%
  mutate(recycling_than_water = ifelse(Importance_recycling_rubbish >	Importance_conserving_water, "Recycling More Important", "Water Conservation More Important"))
```

-->
### Background

Do high school girls text more per week on average than high school boys? This question is interesting because there is sometimes a stereotype that high school girls are always texting. It would be interesting to see if this stereotype holds true when comparing to males of the same age group. To be more precise and formal:

$$
  H_0: \mu_\text{Women} = \mu_\text{Men}
$$
$$ 
  H_a: \mu_\text{Women} \gt \mu_\text{Men}
$$
The level of significance will be set at: 
$$
	\alpha = .05
$$

In this situation, it seems appropriate to perform a two sample independent t-test. Our data comes from the a US Census that was conducted, therefore we can assume that it is a simple random sample. Each group also contains a sample size greater than 30 so because of the central limit theorem we can be sure that the distribution of sample means is normal. With both of these requirements met, we can move on with our study.

### Analysis

We were able to run this analysis using the independent t-test function in R and building some visual representations of the data. What was found is that the data is very strongly right-skewed in both categories, but mostly with the males. Most females text more than the males do based on the median, however the male mean is much higher because of some extremely large outliers up in the 10,000s. To really build an accurate representation with a t-test, we would need to remove these outliers, so the data was filtered to points only below 5000 text-messages sent yesterday. This made the t-test, and even the graphs, much more meaningful.

The box plots help us to explicitly see and compare the median, 25 percentile, and 75th percentile between males and females. The histograms give a better idea of the overall distribution of the data for each group. A version before the filter is even included to give an idea of exactly how much the outliers skewed the data and why they were removed. 
```{r, message=FALSE, warning=FALSE}

yeah <- HSS %>% 
  na.omit(c(Text_Messages_Sent_Yesterday, Gender)) %>% 
  filter(Text_Messages_Sent_Yesterday <5000)

no <- HSS %>% 
  na.omit(c(Text_Messages_Sent_Yesterday, Gender))

pander(favstats(Text_Messages_Sent_Yesterday ~ Gender, data=no)[,-10], caption='See Stats Without Filter')

ggplot(no, aes(x=Gender, y=Text_Messages_Sent_Yesterday)) +
geom_boxplot() +
coord_cartesian(ylim = c(0, 150)) +
labs(title = "Compare Medians Without Filter")

ggplot(no, aes(x=Text_Messages_Sent_Yesterday)) +
  geom_histogram() +
  facet_wrap(~Gender) +
  labs(title = "Compare Distribution Without Filter")

pander(favstats(Text_Messages_Sent_Yesterday ~ Gender, data=yeah)[,-10], caption='See Stats With Filter')

ggplot(yeah, aes(x=Text_Messages_Sent_Yesterday)) +
  geom_histogram() +
  facet_wrap(~Gender) +
  labs(title = "Compare distribution with Filter below 5000")

```
```{r, message=FALSE, warning=FALSE}

pander(t.test(Text_Messages_Sent_Yesterday ~ Gender, data = yeah, mu = 0, alternative = "greater", conf.level = 0.95))
```

### Interpretation

Using R programming we were able to run a t-test. The results are displayed above. Despite the means between the two groups appearing to be very different, the P-value comes out to be .09135 which is not less than our level of significance, so we do not have enough evidence to prove that there is a significant difference between males and females texting. We fail to reject the null. This means that there is not sufficient evidence to prove that high school girls text more than high school boys and it would be incorrect, for now, to perpetuate this sort of stereotype. However, future studies with more data could potentially prove otherwise, or if for some reason we chose to raise our alpha to .1, then we could possibly reject the null in those studies. 

This is a good example of why it is important to use a t-test rather than simply finding and comparing the means of two groups. A human would likely look at the two numbers and say that they are very different but running a t-test gives us the ability to objectively say how different they really are. 







